Monte Carlo and bootstrap for ALL parameters

### 2024-08-08 All_param.Rmd
est_boot not finished

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  for (c in 1:nboot) {
    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```

>>>>

  n <- nrow(df) + 1 # sample size of the initial sample
  nboot <- length(df)/(nb_var+2) # number of bootstrap samples
  vec_est1 <- c()
  vec_est2 <- c()
  vec_est3 <- c()
  # big_vec <- rep(c(), 12)
  for (c in 1:nboot) {
    # mapply(function(vec_, c){append(vec_, (n/(n-1))*sum(df[, 2 + c + ((nb_var+2)*(c-1))]/p))}, big_vec, )
    vec_est1 <- append(vec_est1, (n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p))
    vec_est2 <- append(vec_est2, (n/(n-1))*sum(df[,(nb_var+2)*c]/p))
    vec_est3 <- append(vec_est3, ((n/(n-1))*sum(df[,(nb_var+2)*c]/p))/((n/(n-1))*sum(df[,3 + ((nb_var+2)*(c-1))]/p)))
    # (n/(n-1)) is the correction needed since we choose only (n-1) points
  }
  vec_est <- data.frame(est_nb = vec_est1, est_vol = vec_est2, est_ratio = vec_est3)
  return(vec_est)
  # Data frame with 3 estimations for each sample
}
```
